Tables and Figures - Supplement A, B and C

### 2019-12-13 code/06_Supplement-tables-figures.Rmd
Updated figure for supplement A

```{r, cache = FALSE}
a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2))) + geom_point() + ggtitle("SMD (untransformed)") +
  scale_x_continuous(name = expression(paste(italic(I)^2, "Index"))) +
  scale_y_continuous(name = "Tau")

@@

```{r trunc-biserial, cache = TRUE}
#Transform effect sizes to biserial correlations (pearson's correlations left as is)
#estimate tau2 for correlations
#'transform_MA' and 'summarizer' are sourced functions
res2 <- dat %>%
  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales')) %>%
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map(transform_MA) %>% #
  map_dfr(summarizer, .id = "effect")

#Add rp and k to the data-frame
het <- dat %>%
  select(rp, Site, effect, effect_type) %>%
  group_by(rp, effect) %>%
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>%
  left_join(res2) %>%
  mutate(effect_type = recode(effect_type,
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>%
  ungroup()

@@

```{r c-plot-1, cache = FALSE}
c_plot <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + geom_point() + ggtitle("Point Biserial r (transformed SMD)")

@@

```{r tau-vs-tau}
b <- select(a, effect, tau2) %>%
  left_join(select(d, effect, tau2), by = "effect") #add truncated transformation tau2
```

```{r b-plot-1}
b_plot <- ggplot(b, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) +
  geom_point() +
  ggtitle("SMD vs. Point biserial") +
  scale_x_continuous(name = "Tau (SMD)") +
  scale_y_continuous(name = "Tau (Point biserial)")

@@

_Figure S.1_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into biserial correlations for all effects reported as SMDs in ManyLabs 1. Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text). Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to biserial correlations, either with truncation of correlations over 1 (circles) or without (crosses) when estimating variance. Panel C  shows the associations between estimates of $I^2$ on the SMD metric and estimates of $\tau$ after transformation, either with truncation or not.

>>>>

```{r, cache = FALSE}
a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2))) + geom_point() + ggtitle("SMD (untransformed)") +
  scale_x_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_y_continuous(name = "Tau")

@@

```{r point-biserial, cache = TRUE}
#Transform effect sizes to point-biserial correlations (pearson's correlations left as is)
#estimate tau2 for correlations
#'transform_MA' and 'summarizer' are sourced functions
res2 <- dat %>%
  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "d") %>%
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map(transform_MA) %>% #
  map_dfr(summarizer, .id = "effect")

#Add rp and k to the data-frame
het <- dat %>%
  filter(effect %in% res2$effect) %>% 
  select(rp, Site, effect, effect_type) %>%
  group_by(rp, effect) %>%
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>%
  left_join(res2) %>%
  mutate(effect_type = recode(effect_type,
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>%
  ungroup()

@@

```{r c-plot-1, cache = FALSE}
c_plot <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + 
  geom_point() + 
  scale_y_continuous(name = "Tau") +
  scale_x_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  ggtitle("Point-Biserial r (transformed SMD)")

@@

```{r tau-vs-tau}
b <- select(a, effect, tau2) %>%
  left_join(select(d, effect, tau2), by = "effect") #add point-biserial transformation tau2 to untransformed
```

```{r b-plot-1}
b_plot <- ggplot(b, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) +
  geom_point() +
  ggtitle("SMD vs. Point biserial") +
  scale_x_continuous(name = "Tau (SMD)") +
  scale_y_continuous(name = "Tau (Point-biserial r)")

@@

_Figure S.1_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into point-biserial correlations for all effects reported as SMDs in Many Labs 1. Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text). Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations. Panel C  shows the associations between estimates of $I^2$ on the SMD metric and estimates of $\tau$ after transformation.
